Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
future work, more refs

Let us discuss some avenues for future work.
%
First, we could implement a high-spin version of the GR fitting coefficients to the ParSpec formulas.
%
This has already been done in Ref.~\cite{Carullo:2021dui} extending the validity of the ParSpec formulas up to
spins of $\chi_{\rm f} \approx 0.99$.
%
For the events analyzed here, the original fit by Ref.~\cite{Maselli:2019mjd}
was sufficient, but it might not be the case with future GW events.

@@

~\hscomm{This is a general `limitation' of ringdown test of higher-curvature theories in present detectors.
Point this out in the conclusions after all specific theories are discussed.}

@@

Our work shows that there are theories of gravity (such as dCS) can be unconstrained by studying the
inspiral portion of GW events, {\it yet} can be constrained, if we analyze the ringdown.
%
Our results show that to fulfill the potential to test GR with GW observations,
further work on modeling of the late-inspiral-(plunge)-merger and ringdown of
coalescing BHs  (with NR simulations) and, complementary, the calculations of
QNMs of rapidly-rotating BHs in modified gravity theories (with BH perturbation
theory) are necessary.
%
We hope that our results serve as further motivation to address these
challenging, and outstanding, problems.

>>>>

Let us discuss some avenues for future work.
%
First, we could implement a high-spin version of the GR fitting coefficients to the ParSpec formulas.
%
This has already been done in Ref.~\cite{Carullo:2021dui} extending the validity of the ParSpec formulas up to
spins of $\chi_{\rm f} \approx 0.99$.
%
For the events analyzed here, the original fit by Ref.~\cite{Maselli:2019mjd}
was sufficient, but it might not be the case with upcoming GW observation campaigns.
%
Second, it would be important to incorporate additional effects, such as spin-precession and eccentricity
to \pSEOB~(see e.g., Refs~\cite{Ossokine:2020kjp,Ramos-Buades:2021adz}).

@@

% ~\hscomm{This is a general `limitation' of ringdown test of higher-curvature theories in present detectors.
% Point this out in the conclusions after all specific theories are discussed.}

@@

Our work shows that there are theories of gravity (such as dCS) can be unconstrained by studying the
inspiral portion of GW events, {\it yet} can be constrained, if we analyze the ringdown.
%
Our results show that to fulfill the potential to test GR with GW observations,
further work on modeling of the late-inspiral-(plunge)-merger and ringdown of
coalescing BHs  (with NR simulations) and, complementary, the calculations of
QNMs of rapidly-rotating BHs in modified gravity theories (with BH perturbation
theory) are necessary.
%
We hope that our results can serve as further motivation to address these
outstanding problems.
